### 2019-11-07 report/paper.tex

Throughout the course of the project, we have attempted several different methods with varying degrees of success. While there are several existing computer vision algorithms for face and object detection, such as the "You Only Look Once" object detection~\cite{redmon2016yolo}, these do not seem to work too well with illustrated characters like Waldo, in a complex illustrated iamge. The characters' appearance and size also seems to vary across images, sometimes only a smaller part of the character (i.e a part of the face) is visible. This makes identifying the characters more challenging as well.\\

>>>>

Throughout the course of the project, we have attempted several different methods with varying degrees of success. 
While there are several existing computer vision algorithms for face and object detection, 
such as the YOLO (You Only Look Once) by Redmon et. al. \cite{redmon2016yolo}, these modern approaches
all use Deep Convolutional Neutral Networks, which we were not allowed to use. Therefore we were looking for a "Non-Deep" method.
The characters' appearance and size also seems to vary across images, sometimes only a smaller part of the character (i.e a part of the face) is visible. This makes identifying the characters more challenging as well.\\
